Towards a classification framework for social machines

### 2013-02-21 latex/paper_new.tex
Added more about using the framework

In order to demonstrate usage of our framework's constructs, we ranked our social machines
by their Alexa ranking, and performed a full repertory grid elicitation exercise. The
results are illustrated in a grid and accompanying dendrograms for element and construct
similarity in Figure~\ref{dendrogram}.

@@

[needs some discussion on what this shows.]

>>>>

In order to demonstrate usage of our framework's constructs, we ranked our social machines
by their Alexa ranking, and performed a full repertory grid elicitation exercise over them.
This process involved ranking each social machine against the constructs, rating each construct
from 1 to 5. In total, 680 ranking were made, and the
results are illustrated in a grid and accompanying dendrograms for element and construct
similarity in Figure~\ref{dendrogram}.

@@

From the dendrograms we can get a sense of similarities and separation of social machines. For
instance, it is clear that YouTube, Vimeo, Reddit and Digg are similar, which is logical, because
they are all social machines that focus on sharing content. Likewise, Quora and StackOverflow
are also similar, and again, this makes sense, because they are both question answering social
machines. There is also a dendrogram for the constructs, to show correlations between them. This
dendrogram indicates that there is a correlation between the ``Single Participant Roles'' and
``No Hierarchy in Participant Roles'' constructs, which is because they refer to the same
aspect of social machines. Another, but less obvious similarity is between the ``Large variety of
social features'' and ``Benefit NOT for the world/society'', which indicates that of the social
machines we have rated, there is a correlation between social features and social machines that
do not benefit the world at large, and vice-versa.

We envisage two key initial uses for this framework: for classifying social machines; and for
predicting behaviour of new/future social machines. For classifying social machines, it will
enable direct comparisons to be made with existing machines, as well as provide a platform
for discussions about social machines. We also think that the data from a large-scale classification
exercise may be useful for researchers who wish to apply prediction techniques (such as SVMs)
to social machines, their behaviour and impact.
